\begin{abstract}
\begin{comment}
Due to escalating complexity of hardware design and manufacturing, not only are integrated circuits (ICs) de- signed and fabricated in multiple nations, but also software tools may be supplied worldwide. It makes hardware security become more subject to various kinds of tampering in the sup- ply chain. Hardware Trojan horses (HTHs) can be implanted to facilitate the leakage of confidential information or cause the failure of a system. Reliability Trojan is one of the main catego- ries of HTH attacks because its behavior is progressive and is thus not trivial to be detected, or not considered malicious.
In this work, we propose to insert reliability Trojan into a circuit which can finely control the circuit lifetime as specified by attackers (or even designers), based on manipulating BTI- induced aging behavior in a statistical manner. Experimental results show that, given a specified lifetime target and under the influence of process variations, the circuit is highly likely to fail within a desired lifetime interval. Instead, in a typical de- sign considering pessimistic corners, the resulting lifetime is usually far longer than the target.
\end{comment}
%DATE 2018 Abstract
Device aging, which causes significant loss on circuit performance and lifetime, has been a primary factor in reliability degradation of nanoscale designs. In this paper, we propose to take advantage of aging-induced clock skews (i.e., make them useful for aging tolerance) by manipulating these time-varying skews to compensate for the performance degradation of logic networks. The goal is to assign achievable/reasonable aging-induced clock skews in a circuit, such that its overall performance degradation due to aging can be minimized, that is, the lifespan can be maximized.  On average, 25\% aging tolerance can be achieved with insignificant design overhead. Moreover, we also apply V\textsubscript{th} assignment to further mitigate the aging-induced degradation of logic networks. Averagely, 39.74\% aging tolerance can be achieved when aging manipulation and V\textsubscript{th} assignment are applied.
\end{abstract}