
\section{LIFETIME ESTIMATION}
\label{sec:lt_estimation}
%-------------------------- Paragraph --------------------------------------------------------------------------------------
In this section, we propose a methodology to estimate the lifetime interval of attacked designs, considering the workload variations based on the aforementioned corollary, assumption, and definition of critical operational mode.

It is worth reminding that, the corollary says the union of critical operational modes of all candidate paths is equivalent to the universal set of operational modes, i.e., all operational modes. Thus, to consider all operational modes, we have to consider the severe aging of each candidate path. If the candidate path is considered undergoing severe aging, i.e., the associated critical operational modes are considered applied on the attacked designs, then we can predict the lifetime of other paths using a binary search method, which is explained as follows using an example:

Given the candidate path $i$, the other path $j$, and time variable $t$, the goal of the method is to predict $j's$ lifetime by binarily searching for a convergent $t$. That is, when $t$ converges at the end of binary search, $j's$ lifetime equals the value of $t$. The time variable $t$ changes during the binary search, depending on whether $j's$ setup timing constraint is violated based on Equation~(\ref{eq:setup}), where $j's$ aging rate is derived by the aging correlation between $i$ and $j$ (i.e., regression equation of $i$ on $j$) and $i's$ aging rate is derived using Equation~(\ref{eq:worst}). 

In addition to path $j$, the other path's lifetime can also be derived, using the regression equations of $i$ on them and using the binary search method. As a result, when $i$ is considered undergoing severe aging, we can obtain the other paths' lifetime, among which we choose the smallest one as the lifetime of the attacked design.

Whenever one candidate path is considered undergoing severe aging, we can derive one lifetime value of the attacked design. By considering all candidate paths\footnote{If one candidate path is considered undergoing severe aging, the associated critical operational modes are considered applied on the design. Thus, by considering all candidate paths, all operational modes are considered based on the corollary}, we can find a group of lifetime values, among which smallest one and biggest one are the resulting interval found based on this given attack.


  
